Effect of the Nominal Value of Foreign Currencies in valuing a good

### 2024-04-17 paper.qmd
final draft

Experience suggests that we treat foreign currencies differently to our home currency and have difficulty adjusting to them. Previous research, such as the "money illusion" effect [@cite] suggests that individuals are biased towards the nominal (or face value) of prices. This bias has also been explored in the context foreign currencies, with research finding systematic effects that arise based on the numerousity of values in a foreign currency compared to individuals' home currencies. However, previous research is split on how and why this effect occurs.

@@

This paper aims to build on the aforementioned research in several important ways. Foremost, previous research is conclusive that there is an effect that using foreign currencies has on individuals' consumption behaviour relative to using their home currencies, but is divided on the direction of this effect. Hence, this paper attempts to evaluate the different models posed and use a study to test which model most adequately predicts the perceived behaviour. Second, previous research has only assigned minor significance to using incentive-compatible mechanisms to elicit true preferences of participants. These mechanisms have been established to elicit more accurate responses from participants that are closer to their true preferences [@cite]. Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to elicit participants' willingness to pay (WTP).[^ The BDM mechanism will be defined and explained in more detail in the Methodology section below.] Raghubir and Srivastava [@Raghubir2002] expressed the concern that "despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise. For instance, when people actually exchange foreign currency they may feel richer or poorer depending on the exchange rate, and the differences in perceptions of wealth may affect product valuation". Similarly, Fang [@Fang2019] noted that implementing the BDM mechanism was infeasible for the study he conducted but that future research should focus on using something like it to elicit WTP. Finally, this paper aims to extend the previous literature on the effects of using virtual currencies specifically, due to their increasing rise in importance when transacting or making purchasing decisions online, and determine whether spending behaviour differs when using them.

@@

Standard consumer choice theory suggests that individuals formulate valuations of goods in relation to reference points, such as their budget [@cite]. Specifically, standard theory poses that consumers evaluate their valuation for a good as a ratio to their budget in order to determine what proportion of their spending power is required to purchase the good. To formulate valuations of goods in a different currency, consumers would first determine the value of the good in their home currency and subsequently apply the exchange rate to get their valuation in the foreign currency. Hence, the model follows a two step process:

@@

In designing the main part of the experiment, I chose to conduct an auction, specifically using the BDM mechanism, in order to have an incentive-compatible method of eliciting the participants' WTP. The BDM's incentive compatibility in eliciting WTP is a well-established phenomenon that is superior to using participants' stated preferences [@cite]. The BDM is essentially a sealed-bid, second price auction that is, in its' most common variant, played against a computer drawing a bid from a known distribution. If the players' bid is greater than or equal to the computers' bid, they win and pay the computers' bid, otherwise they lose. As mentioned above, the studies conducted by Raghubir and Srivastava [@Raghubir2002], Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007] (with the exception of one permutation of one of the studies) and Fang [@Fang2019] did not implement incentive-compatible methods of eliciting the participants' preferences, making this experiment an important addition to these previous studies in examining whether the effects described still hold when a more truthful way of eliciting WTP is used. In order to incentivise the participants to participate, I ran a lottery that paid out three randomly-chosen participants based on their actual choices made in the auction and by simulating the BDM mechanism using a random number generator. Due to budget constraints, I was only able to play this lottery for three people, but given that the sample size of the experiment was relatively small, the potential to receive one's outcome is likely to have helped in eliciting the participants' true WTP.

@@

In setting up the experiment, I incorrectly used the BDM mechanism. Instead of explaining it as a sealed-bid second-price auction, the experiment instructions explained it as a sealed-bid first-price auction. Unlike in a second-price auction, the participants of a first price auction do not have a (weakly) dominant strategy to bid their true valuations, in fact there generally is no dominant strategy in such an auction [@cite]. This is true even in this auction in which participants knew that they were bidding against a computer agent who would randomly draw a bid from a uniform distribution from 0-50, with an expected bid of 25. Indeed, the optimal strategy by participants was to choose their bid b by maximising their payoff p:

@@

summary(experiment_data$group_multiple_bid_in_pounds)
sd(experiment_data$group_multiple_bid_in_pounds, na.rm = TRUE)
```

@@

# Perform a t-test to compare the means of the two groups
t.test(
    experiment_data$group_fraction_bid_in_pounds,
    experiment_data$group_multiple_bid_in_pounds
)
```

@@

To investigate this further, I have conducted a power analysis in order to determine the power of the t-test, which refers to the likelihood of the test detecting a true positive when an effect actually exists [@cite]. High power would indicate that this likelihood is high and vice versa. To conduct the analysis, we first need to find the effect size, or Cohen's D, and then implement the power analysis. Further, I will also conduct an analysis that investigates how big the sample size should have been to get a power of 80%, which is a generally accepted threshold for significant power.

@@

Finally, I conducted a regression of the demographic values collected in the fourth part of the experiment on the bids of each group. This is done in order to determine whether there is any correlation between the demographic variables and the bid amount, which would suggest that randomisation did not occur correctly, which could have been exacerbated by the small sample size. The regression yields the following outcomes:

Based on this regression, there are no statistically significant correlations at the 5% significance level or lower. However, there is one correlation that is significant at the 10% significance level, namely of `expenditure£551-£700` on the multiple group. The coefficient of -43.487 suggests that people whose usual expenditure is between £551 and £700 per month bid lower than the group overall. However, given that this is only significant at the 10% level and not at any lower ones, it is likely that this correlation is due to the low sample size rather than it representing a true correlation between these variables.

@@

@@

![Consent](experiment_instructions/consent.png)

>>>>

Experience suggests that we treat foreign currencies differently to our home currency and have difficulty adjusting to them. Previous research, such as the "money illusion" effect [@Shafir1997] suggests that individuals are biased towards the nominal (or face value) of prices. This bias has also been explored in the context foreign currencies, with research finding systematic effects that arise based on the numerousity of values in a foreign currency compared to individuals' home currencies. However, previous research is split on how and why this effect occurs.

@@

This paper aims to build on the aforementioned research in several important ways. Foremost, previous research is conclusive that there is an effect that using foreign currencies has on individuals' consumption behaviour relative to using their home currencies, but is divided on the direction of this effect. Hence, this paper attempts to evaluate the different models posed and use a study to test which model most adequately predicts the perceived behaviour. Second, previous research has only assigned minor significance to using incentive-compatible mechanisms to elicit true preferences of participants. These mechanisms have been established to elicit more accurate responses from participants that are closer to their true preferences [@Burchardi2021]. Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to elicit participants' willingness to pay (WTP).^[ The BDM mechanism will be defined and explained in more detail in the Methodology section below.] Raghubir and Srivastava [@Raghubir2002] expressed the concern that "despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise. For instance, when people actually exchange foreign currency they may feel richer or poorer depending on the exchange rate, and the differences in perceptions of wealth may affect product valuation". Similarly, Fang [@Fang2019] noted that implementing the BDM mechanism was infeasible for the study he conducted but that future research should focus on using something like it to elicit WTP. Finally, this paper aims to extend the previous literature on the effects of using virtual currencies specifically, due to their increasing rise in importance when transacting or making purchasing decisions online, and determine whether spending behaviour differs when using them.

@@

Standard consumer choice theory suggests that individuals formulate valuations of goods in relation to reference points, such as their budget [@Deaton1980]. Specifically, standard theory poses that consumers evaluate their valuation for a good as a ratio to their budget in order to determine what proportion of their spending power is required to purchase the good. To formulate valuations of goods in a different currency, consumers would first determine the value of the good in their home currency and subsequently apply the exchange rate to get their valuation in the foreign currency. Hence, the model follows a two step process:

@@

In designing the main part of the experiment, I chose to conduct an auction, specifically using the BDM mechanism, in order to have an incentive-compatible method of eliciting the participants' WTP. The BDM's incentive compatibility in eliciting WTP is a well-established phenomenon that is superior to using participants' stated preferences [@Burchardi2021]. The BDM is essentially a sealed-bid, second price auction that is, in its' most common variant, played against a computer drawing a bid from a known distribution. If the players' bid is greater than or equal to the computers' bid, they win and pay the computers' bid, otherwise they lose. As mentioned above, the studies conducted by Raghubir and Srivastava [@Raghubir2002], Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007] (with the exception of one permutation of one of the studies) and Fang [@Fang2019] did not implement incentive-compatible methods of eliciting the participants' preferences, making this experiment an important addition to these previous studies in examining whether the effects described still hold when a more truthful way of eliciting WTP is used. In order to incentivise the participants to participate, I ran a lottery that paid out three randomly-chosen participants based on their actual choices made in the auction and by simulating the BDM mechanism using a random number generator. Due to budget constraints, I was only able to play this lottery for three people, but given that the sample size of the experiment was relatively small, the potential to receive one's outcome is likely to have helped in eliciting the participants' true WTP.

@@

In setting up the experiment, I incorrectly used the BDM mechanism. Instead of explaining it as a sealed-bid second-price auction, the experiment instructions explained it as a sealed-bid first-price auction. Unlike in a second-price auction, the participants of a first price auction do not have a (weakly) dominant strategy to bid their true valuations, in fact there generally is no dominant strategy in such an auction [@Noussair2004]. This is true even in this auction in which participants knew that they were bidding against a computer agent who would randomly draw a bid from a uniform distribution from 0-50, with an expected bid of 25. Indeed, the optimal strategy by participants was to choose their bid b by maximising their payoff p:

@@

# Summary statistics for the bid columns
summary(experiment_data$group_fraction_bid_in_pounds)

summary(experiment_data$group_multiple_bid_in_pounds)
```

@@

# Perform a t-test to compare the means of the two groups
t_test <- t.test(
    experiment_data$group_fraction_bid_in_pounds,
    experiment_data$group_multiple_bid_in_pounds
)
cat(paste("t =", t_test$statistic, "\n"))
cat(paste("p-value =", t_test$p.value))
cat("95 percent confidence interval: \n")
cat(paste(t_test$conf.int))
```

@@

To investigate this further, I have conducted a power analysis in order to determine the power of the t-test, which refers to the likelihood of the test detecting a true positive when an effect actually exists. High power would indicate that this likelihood is high and vice versa. To conduct the analysis, we first need to find the effect size, or Cohen's D, and then implement the power analysis. Further, I will also conduct an analysis that investigates how big the sample size should have been to get a power of 80%, which is a generally accepted threshold for significant power.

@@

Finally, I conducted a regression of the demographic values collected in the fourth part of the experiment on the bids of each group. This is done in order to determine whether there is any correlation between the demographic variables and the bid amount, which would suggest that randomisation did not occur correctly, which could have been exacerbated by the small sample size.^[ For brevity, the regression output has been moved into the appendix.] Based on this regression, there are no statistically significant correlations at the 5% significance level or lower. However, there is one correlation that is significant at the 10% significance level, namely of `expenditure£551-£700` on the multiple group. The coefficient of -43.487 suggests that people whose usual expenditure is between £551 and £700 per month bid lower than the group overall. However, given that this is only significant at the 10% level and not at any lower ones, it is likely that this correlation is due to the low sample size rather than it representing a true correlation between these variables.

@@

## Regression output

@@

{{< pagebreak >}}

### 2024-04-17 paper.tex
final draft

Experience suggests that we treat foreign currencies differently to our
home currency and have difficulty adjusting to them. Previous research,
such as the ``money illusion'' effect (\textbf{cite?}) suggests that
individuals are biased towards the nominal (or face value) of prices.
This bias has also been explored in the context foreign currencies, with
research finding systematic effects that arise based on the numerousity
of values in a foreign currency compared to individuals' home
currencies. However, previous research is split on how and why this
effect occurs.

@@

This paper aims to build on the aforementioned research in several
important ways. Foremost, previous research is conclusive that there is
an effect that using foreign currencies has on individuals' consumption
behaviour relative to using their home currencies, but is divided on the
direction of this effect. Hence, this paper attempts to evaluate the
different models posed and use a study to test which model most
adequately predicts the perceived behaviour. Second, previous research
has only assigned minor significance to using incentive-compatible
mechanisms to elicit true preferences of participants. These mechanisms
have been established to elicit more accurate responses from
participants that are closer to their true preferences (\textbf{cite?}).
Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to
elicit participants' willingness to pay (WTP).{[}\^{} The BDM mechanism
will be defined and explained in more detail in the Methodology section
below.{]} Raghubir and Srivastava (Raghubir and Srivastava 2002)
expressed the concern that ``despite attempts to make the tasks as
realistic as possible, the studies reported were laboratory experiments,
and issues of generalizability when real money is on the line do arise.
For instance, when people actually exchange foreign currency they may
feel richer or poorer depending on the exchange rate, and the
differences in perceptions of wealth may affect product valuation''.
Similarly, Fang (Fang 2019) noted that implementing the BDM mechanism
was infeasible for the study he conducted but that future research
should focus on using something like it to elicit WTP. Finally, this
paper aims to extend the previous literature on the effects of using
virtual currencies specifically, due to their increasing rise in
importance when transacting or making purchasing decisions online, and
determine whether spending behaviour differs when using them.

@@

Standard consumer choice theory suggests that individuals formulate
valuations of goods in relation to reference points, such as their
budget (\textbf{cite?}). Specifically, standard theory poses that
consumers evaluate their valuation for a good as a ratio to their budget
in order to determine what proportion of their spending power is
required to purchase the good. To formulate valuations of goods in a
different currency, consumers would first determine the value of the
good in their home currency and subsequently apply the exchange rate to
get their valuation in the foreign currency. Hence, the model follows a
two step process:

@@

In designing the main part of the experiment, I chose to conduct an
auction, specifically using the BDM mechanism, in order to have an
incentive-compatible method of eliciting the participants' WTP. The
BDM's incentive compatibility in eliciting WTP is a well-established
phenomenon that is superior to using participants' stated preferences
(\textbf{cite?}). The BDM is essentially a sealed-bid, second price
auction that is, in its' most common variant, played against a computer
drawing a bid from a known distribution. If the players' bid is greater
than or equal to the computers' bid, they win and pay the computers'
bid, otherwise they lose. As mentioned above, the studies conducted by
Raghubir and Srivastava (Raghubir and Srivastava 2002), Wertenbroch,
Soman and Chattopadhyay (Wertenbroch, Soman, and Chattopadhyay 2007)
(with the exception of one permutation of one of the studies) and Fang
(Fang 2019) did not implement incentive-compatible methods of eliciting
the participants' preferences, making this experiment an important
addition to these previous studies in examining whether the effects
described still hold when a more truthful way of eliciting WTP is used.
In order to incentivise the participants to participate, I ran a lottery
that paid out three randomly-chosen participants based on their actual
choices made in the auction and by simulating the BDM mechanism using a
random number generator. Due to budget constraints, I was only able to
play this lottery for three people, but given that the sample size of
the experiment was relatively small, the potential to receive one's
outcome is likely to have helped in eliciting the participants' true
WTP.

@@

In setting up the experiment, I incorrectly used the BDM mechanism.
Instead of explaining it as a sealed-bid second-price auction, the
experiment instructions explained it as a sealed-bid first-price
auction. Unlike in a second-price auction, the participants of a first
price auction do not have a (weakly) dominant strategy to bid their true
valuations, in fact there generally is no dominant strategy in such an
auction (\textbf{cite?}). This is true even in this auction in which
participants knew that they were bidding against a computer agent who
would randomly draw a bid from a uniform distribution from 0-50, with an
expected bid of 25. Indeed, the optimal strategy by participants was to
choose their bid b by maximising their payoff p:

@@

\begin{verbatim}
[1] 15.49001
\end{verbatim}

@@

\begin{verbatim}
[1] 14.8083
\end{verbatim}

@@

    Welch Two Sample t-test

data:  experiment_data$group_fraction_bid_in_pounds and experiment_data$group_multiple_bid_in_pounds
t = -1.2323, df = 38.999, p-value = 0.2252
alternative hypothesis: true difference in means is not equal to 0
95 percent confidence interval:
 -15.401901   3.740092
sample estimates:
mean of x mean of y 
  19.7381   25.5690 
\end{verbatim}

@@

To investigate this further, I have conducted a power analysis in order
to determine the power of the t-test, which refers to the likelihood of
the test detecting a true positive when an effect actually exists
(\textbf{cite?}). High power would indicate that this likelihood is high
and vice versa. To conduct the analysis, we first need to find the
effect size, or Cohen's D, and then implement the power analysis.
Further, I will also conduct an analysis that investigates how big the
sample size should have been to get a power of 80\%, which is a
generally accepted threshold for significant power.

@@

Finally, I conducted a regression of the demographic values collected in
the fourth part of the experiment on the bids of each group. This is
done in order to determine whether there is any correlation between the
demographic variables and the bid amount, which would suggest that
randomisation did not occur correctly, which could have been exacerbated
by the small sample size. The regression yields the following outcomes:

Based on this regression, there are no statistically significant
correlations at the 5\% significance level or lower. However, there is
one correlation that is significant at the 10\% significance level,
namely of \texttt{expenditure£551-£700} on the multiple group. The
coefficient of -43.487 suggests that people whose usual expenditure is
between £551 and £700 per month bid lower than the group overall.
However, given that this is only significant at the 10\% level and not
at any lower ones, it is likely that this correlation is due to the low
sample size rather than it representing a true correlation between these
variables.

@@

@@

@@

@@

@@

@@

{\centering \includegraphics{experiment_instructions/consent.png}

\caption{Consent}

@@

The full source code of data analysis is follows:

>>>>

Experience suggests that we treat foreign currencies differently to our
home currency and have difficulty adjusting to them. Previous research,
such as the ``money illusion'' effect (Shafir, Diamond, and Tversky
1997) suggests that individuals are biased towards the nominal (or face
value) of prices. This bias has also been explored in the context
foreign currencies, with research finding systematic effects that arise
based on the numerousity of values in a foreign currency compared to
individuals' home currencies. However, previous research is split on how
and why this effect occurs.

@@

This paper aims to build on the aforementioned research in several
important ways. Foremost, previous research is conclusive that there is
an effect that using foreign currencies has on individuals' consumption
behaviour relative to using their home currencies, but is divided on the
direction of this effect. Hence, this paper attempts to evaluate the
different models posed and use a study to test which model most
adequately predicts the perceived behaviour. Second, previous research
has only assigned minor significance to using incentive-compatible
mechanisms to elicit true preferences of participants. These mechanisms
have been established to elicit more accurate responses from
participants that are closer to their true preferences (Burchardi et al.
2021). Hence, this study will use the Becker-DeGroot-Marshak (BDM)
mechanism to elicit participants' willingness to pay (WTP).\footnote{
  The BDM mechanism will be defined and explained in more detail in the
  Methodology section below.} Raghubir and Srivastava (Raghubir and
Srivastava 2002) expressed the concern that ``despite attempts to make
the tasks as realistic as possible, the studies reported were laboratory
experiments, and issues of generalizability when real money is on the
line do arise. For instance, when people actually exchange foreign
currency they may feel richer or poorer depending on the exchange rate,
and the differences in perceptions of wealth may affect product
valuation''. Similarly, Fang (Fang 2019) noted that implementing the BDM
mechanism was infeasible for the study he conducted but that future
research should focus on using something like it to elicit WTP. Finally,
this paper aims to extend the previous literature on the effects of
using virtual currencies specifically, due to their increasing rise in
importance when transacting or making purchasing decisions online, and
determine whether spending behaviour differs when using them.

@@

Standard consumer choice theory suggests that individuals formulate
valuations of goods in relation to reference points, such as their
budget (Deaton and Muellbauer 1980). Specifically, standard theory poses
that consumers evaluate their valuation for a good as a ratio to their
budget in order to determine what proportion of their spending power is
required to purchase the good. To formulate valuations of goods in a
different currency, consumers would first determine the value of the
good in their home currency and subsequently apply the exchange rate to
get their valuation in the foreign currency. Hence, the model follows a
two step process:

@@

In designing the main part of the experiment, I chose to conduct an
auction, specifically using the BDM mechanism, in order to have an
incentive-compatible method of eliciting the participants' WTP. The
BDM's incentive compatibility in eliciting WTP is a well-established
phenomenon that is superior to using participants' stated preferences
(Burchardi et al. 2021). The BDM is essentially a sealed-bid, second
price auction that is, in its' most common variant, played against a
computer drawing a bid from a known distribution. If the players' bid is
greater than or equal to the computers' bid, they win and pay the
computers' bid, otherwise they lose. As mentioned above, the studies
conducted by Raghubir and Srivastava (Raghubir and Srivastava 2002),
Wertenbroch, Soman and Chattopadhyay (Wertenbroch, Soman, and
Chattopadhyay 2007) (with the exception of one permutation of one of the
studies) and Fang (Fang 2019) did not implement incentive-compatible
methods of eliciting the participants' preferences, making this
experiment an important addition to these previous studies in examining
whether the effects described still hold when a more truthful way of
eliciting WTP is used. In order to incentivise the participants to
participate, I ran a lottery that paid out three randomly-chosen
participants based on their actual choices made in the auction and by
simulating the BDM mechanism using a random number generator. Due to
budget constraints, I was only able to play this lottery for three
people, but given that the sample size of the experiment was relatively
small, the potential to receive one's outcome is likely to have helped
in eliciting the participants' true WTP.

@@

In setting up the experiment, I incorrectly used the BDM mechanism.
Instead of explaining it as a sealed-bid second-price auction, the
experiment instructions explained it as a sealed-bid first-price
auction. Unlike in a second-price auction, the participants of a first
price auction do not have a (weakly) dominant strategy to bid their true
valuations, in fact there generally is no dominant strategy in such an
auction (Noussair, Robin, and Ruffieux 2004). This is true even in this
auction in which participants knew that they were bidding against a
computer agent who would randomly draw a bid from a uniform distribution
from 0-50, with an expected bid of 25. Indeed, the optimal strategy by
participants was to choose their bid b by maximising their payoff p:

@@

@@

@@

\begin{verbatim}
t = -1.23227791692727 
\end{verbatim}

\begin{verbatim}
p-value = 0.225223137738591
\end{verbatim}

\begin{verbatim}
95 percent confidence interval: 
\end{verbatim}

\begin{verbatim}
-15.4019012943159 3.74009177050641
\end{verbatim}

@@

To investigate this further, I have conducted a power analysis in order
to determine the power of the t-test, which refers to the likelihood of
the test detecting a true positive when an effect actually exists. High
power would indicate that this likelihood is high and vice versa. To
conduct the analysis, we first need to find the effect size, or Cohen's
D, and then implement the power analysis. Further, I will also conduct
an analysis that investigates how big the sample size should have been
to get a power of 80\%, which is a generally accepted threshold for
significant power.

@@

Finally, I conducted a regression of the demographic values collected in
the fourth part of the experiment on the bids of each group. This is
done in order to determine whether there is any correlation between the
demographic variables and the bid amount, which would suggest that
randomisation did not occur correctly, which could have been exacerbated
by the small sample size.\footnote{ For brevity, the regression output
  has been moved into the appendix.} Based on this regression, there are
no statistically significant correlations at the 5\% significance level
or lower. However, there is one correlation that is significant at the
10\% significance level, namely of \texttt{expenditure£551-£700} on the
multiple group. The coefficient of -43.487 suggests that people whose
usual expenditure is between £551 and £700 per month bid lower than the
group overall. However, given that this is only significant at the 10\%
level and not at any lower ones, it is likely that this correlation is
due to the low sample size rather than it representing a true
correlation between these variables.

@@

\bibitem[\citeproctext]{ref-Burchardi2021}
Burchardi, Konrad B., Jonathan de Quidt, Selim Gulesci, Benedetta Lerva,
and Stefano Tripodi. 2021. {`Testing Willingness to Pay Elicitation
Mechanisms in the Field: Evidence from Uganda'}. \emph{Journal of
Development Economics} 152: 102701.
https://doi.org/\url{https://doi.org/10.1016/j.jdeveco.2021.102701}.

\bibitem[\citeproctext]{ref-Deaton1980}
Deaton, Angus, and John Muellbauer. 1980. \emph{Economics and Consumer
Behavior}. Cambridge University Press.

@@

\bibitem[\citeproctext]{ref-Noussair2004}
Noussair, Charles, Stephane Robin, and Bernard Ruffieux. 2004.
{`Revealing Consumers' Willingness-to-Pay: A Comparison of the BDM
Mechanism and the Vickrey Auction'}. \emph{Journal of Economic
Psychology} 25 (6): 725--41.
https://doi.org/\url{https://doi.org/10.1016/j.joep.2003.06.004}.

@@

\bibitem[\citeproctext]{ref-Shafir1997}
Shafir, Eldar, Peter Diamond, and Amos Tversky. 1997. {`Money
Illusion'}. \emph{The Quarterly Journal of Economics} 112 (2): 341--74.
\url{http://www.jstor.org/stable/2951239}.

@@

\section{Regression output}\label{regression-output}

@@

\newpage{}

@@

@@

The full source code of the data analysis is follows:
